%================Thesis Abstract===============
\begin{center}
\Large{\textbf{ABSTRACT}}\\
\end{center}
%=============================================
My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.My abstract.My abstract. My abstract.My abstract. My abstract.My abstract. My abstract.My abstract.

% Refer to ACM Computing Classification System Taxonomy, read first page and following the instruction given therein.=============
\par 
\textbf{[Security and Privacy]}: Cryptography—key management, symmetric cryptography; Security Services—authentication, access control

